Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-14 paper.tex
Add a note about term orders

>>>>

Requirement~\ref{cond:match:closed} implies that we will be adding hypotheses to matches in the order in which the slots appear.
Hence for a rule $r : A → B → C → D$, we effectively consider partial applications $r~a$ and $r~a~b$ for some $a : A$ and $b : B$, but not $r~\text{--}~b$.
This prevents us from constructing $r~a~b$ in two different but ultimately redundant ways.
The term orders used in various saturation calculi serve a similar function.
